Aspects of RDF Data Constraints in the Social, Behavioural and Economic Sciences

### 2015-04-30 paper/paper7/paper7.tex
evaluation

63\% of all violations are caused by \emph{warning constraints} which are only 10\% of all constraints. 
Only 6\% of the violations are caused by \emph{error constraints} which are 49\% of all constraints.

\begin{hyp}
In general, data quality is high (according to severity levels) since only 6\% of the violations are caused by error constraints which are 49\% of all defined constraints.
\end{hyp}

\begin{hyp}
The percentage of severe violations is very low (6\%), compared to about 2/3 of warning violations and 1/3 of informational violations, which implies that proper constraint languages can significantly improve the data quality beyond fundamental requirements.
\end{hyp}

>>>>

2/3 of all violations are caused by \emph{warning constraints} which are only 10\% of all constraints. 
Only 6\% of the violations are caused by \emph{error constraints} which are 49\% of all constraints.
1/3 of all violations are raised by informational constraints.
This means that in general, data quality is high with regard to the severity level of constraints.

\begin{hyp}
The percentage of severe violations is very low, compared to about 2/3 of warning violations and 1/3 of informational violations, which implies that proper constraint languages can significantly improve the data quality beyond fundamental requirements.
\end{hyp}
